The \dealii Library, Version 9.7

### 2025-07-19 9.7/paper.tex
Update numbers.

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release: Around 130 of the more than 1600 (non-merge)
commits that went into this release touched the tutorial.
% data generated using these commands:
% - tutorial: git log --since 2023/07/07 --until 2024/08/11 --no-merges examples | grep commit | wc -l
% - total:    git log --since 2023/07/07 --until 2024/08/11 --no-merges | grep commit | wc -l
In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \step{93}
    demonstrates how one can implement problems in which some of the
    variables to be solved for are not degrees of freedom of a finite
    element field (so-called ``non-local'' degrees of freedom, because
    they have no associated node functional that is tied to a cell or
    a patch of cells). Specifically, the program solves an
    optimization problem in which some of the variables are scalars
    that multiply certain source terms.
    \step{93} was written by Sam Scheuerman.
  \item
    \step{95} illustrates the use of matrix-free methods to solve
    problems with embedded boundaries using the CutFEM method that was
    previously already introduced in \step{85}. \step{95} was written
    by Maximilian Bergbauer, with help by Martin Kronbichler and Peter Munch.
  \item
    \step{97}
    is a program that solves a curl-curl problem from electromagnetics
    -- more specifically, from magnetostatics. The program shows a
    formulation in which two curl-curl problems are solved
    consecutively to model the magnetic field that results from the
    current in an electrically conducting coil.
    \step{97} was written by Siarhei Uzunbajakau.
\end{itemize}

>>>>

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release: Around 125 of the more than 1500 (non-merge)
commits that went into this release touched the tutorial.
% data generated using these commands:
% - tutorial: git log --since 2024/08/11 --until 2025/07/19 --no-merges examples | grep commit | wc -l
% - total:    git log --since 2024/08/11 --until 2025/07/19 --no-merges | grep commit | wc -l
In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \step{93}
    demonstrates how one can implement problems in which some of the
    variables to be solved for are not degrees of freedom of a finite
    element field (so-called ``non-local'' degrees of freedom, because
    they have no associated node functional that is tied to a cell or
    a patch of cells). Specifically, the program solves an
    optimization problem in which some of the variables are scalars
    that multiply certain source terms.
    \step{93} was written by Sam Scheuerman.
  \item
    \step{95} illustrates the use of matrix-free methods to solve
    problems with embedded boundaries using the CutFEM method that was
    previously already introduced in \step{85}. \step{95} was written
    by Maximilian Bergbauer, with help by Martin Kronbichler and Peter Munch.
  \item
    \step{97}
    is a program that solves a curl-curl problem from electromagnetics
    -- more specifically, from magnetostatics. The program shows a
    formulation in which two curl-curl problems are solved
    consecutively to model the magnetic field that results from the
    current in an electrically conducting coil.
    \step{97} was written by Siarhei Uzunbajakau.
\end{itemize}
